Quantifying the rock-paper-scissors effect

### 2024-05-29 inst/rock_paper_scissors_monster.Rmd
bugfix

```{r,label=defineh3seven}
H3seven <- function(lambda){
  H3 <- hyper3()
  for(i in 1:6){
     jj <- 1  # diagonal players do not have lambda-advantage
     names(jj) <- tt[i]
     H3[jj] %<>% inc(hw[i,i])
     H3[setNames(1,tt[i])] %<>% inc(hw[i,i])

>>>>

```{r,label=defineh3seven}
H3seven <- function(lambda){
  H3 <- hyper3()
  for(i in 1:6){
     jj <- 1  # diagonal players do not have lambda-advantage
     names(jj) <- tt[i]
     H3[jj] %<>% inc(hw[i,i])
